### 2019-10-21 paper/paper.tex
Updates from Overleaf

\begin{lstlisting}[language = Julia]
# perform a merge sort on `v` using parallel threads
function psort(v::AbstractVector)
    hi = length(v)
    if hi < 100_000 # below some cutoff, run in serial
        return sort(view(v, 1:hi), alg = MergeSort)
    end
# split the range and sort the halves in parallel recursively
    mid = (1 + hi) >>> 1
    half = Threads.@spawn psort(view(v, 1:mid))
    right = psort(view(v, (mid + 1):hi))
    left = fetch(half)::typeof(right)
# perform the merge on the result
    out = similar(v)
    i, il, ir = 1, 1, 1
    @inbounds while il <= mid && ir <= (hi - mid)
        l, r = left[il], right[ir]
        if l < r
            out[i] = l
            il += 1
        else
            out[i] = r
            ir += 1
        end
        i += 1
    end
    @inbounds while il <= length(left)
        out[i] = left[il]
        il += 1
        i += 1
    end
    @inbounds while ir <= length(right)
        out[i] = right[ir]
        ir += 1
        i += 1
    end
    return out
end
\end{lstlisting}

>>>>

\begin{lstlisting}[language = Julia]
# perform a merge sort on `v` using parallel threads
function psort(v::AbstractVector)
    hi = length(v)
    if hi < 100_000 # below some cutoff, run in serial
        return sort(view(v, 1:hi), alg = MergeSort)
    end
# split the range and sort the halves in parallel recursively
    mid = (1 + hi) >>> 1
    half = Threads.@spawn psort(view(v, 1:mid))
    right = psort(view(v, (mid + 1):hi))
    left = fetch(half)::typeof(right)
# perform the merge on the result
    out = similar(v)
    i, il, ir = 1, 1, 1
    @inbounds while il <= mid && ir <= (hi - mid)
        l, r = left[il], right[ir]
        if r < l
            out[i] = r
            ir += 1
        else
            out[i] = l
            il += 1
        end
        i += 1
    end
    @inbounds while il <= length(left)
        out[i] = left[il]
        il += 1
        i += 1
    end
    @inbounds while ir <= length(right)
        out[i] = right[ir]
        ir += 1
        i += 1
    end
    return out
end
\end{lstlisting}
